--- 
title: "Кратенькая жизнеописаловка"
author: "НеХотаббыч"  
date: " `r format(Sys.time(), '%d %b. %Y г.')` "
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
lang: "ru"
fontfamily: accanthis
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."  
mainfont: Georgia
monofont: "Courier New"
monofontoptions: "Scale=0.7"
fontsize: 12pt
papersize: a4
geometry:
  - top=1in
  - left=0.7in
  - right=0.7in
  - bottom=1in  
---

# Введение

Чего введение я так и не понял, ну, да, ладно, пусть будет...  

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
